Revisiting Multi-Domain Machine Translation

### 2020-04-29 2020/coling2020/multidomain.tex

\begin{table*}
  \centering
  \fyDone{Fix column size}
  \begin{tabular}{|p{3cm}|*{8}{r|}|} \hline
%     &&&&&& \\
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{\domain{avg}} & \multicolumn{1}{c||}{w\domain{avg}} \\ \hline % & \multicolumn{1}{c|}{\domain{news}} 
  %    \system{Mixed-Nat}  & 37.3 & 54.6 & 50.1 & 33.5 & 43.2 & 77.5  & 41.1  & 49.4 \\% & 23.5\\
  %     \system{FT-Full}       & 37.7 & \SB{59.2} & \SB{54.5} & 34.0 & \SB{46.8} & \SB{90.8}   & 42.8 & 53.8\\
  %   Full-finetuned on extended in-domain corpora (news) & && 33.96&&& & &\\nn
    \system{DC-Tag}       & 38.5 & \SW{54.0} & 49.0   & 33.6 & \SW{42.2} & \SW{76.7} & 49.0 & 41.6 \\%    & 21.8 \\
    \system{DC-Feat}      & 37.3  & 54.2 & 49.3   & 33.6 & \SW{41.9} & \SW{75.8} & 48.3 & 40.7  \\% & \SW{21.7} \\
    \system{LDC-Tag}     & 37.4   & 54.1 & \SW{48.7} & \SW{32.5} & \SW{41.4} & \SW{75.9} & 48.3 & 39.1         \\% & 22.1 \\ 
    \system{TTM}            & 37.4 & \SW{53.7} & 48.9 & 32.8 & 41.3 & \SW{75.8} & 48.3 & 40.7   \\% &  23.4 \\
    \system{DM}             & 35.4 & 49.3  & 45.2 & 29.7 & 37.1 & \SW{60.0} & 42.8 & 37.8 \\ % & 22.6\\
    \system{ADM}           & 36.1 & 53.5  & 48.0 & 32.0 & 41.1 & 72.1 & 47.1 & 39.5\\% & 23.3 \\
    \system{WDCMT}       & 36.0 & 53.8 & 48.5 & 31.0 & 39.0 & 63.5 & 45.3 & 39.1\\ % & 20.4 \\
    \system{MDL Res}     & 37.3 & 55.5  & \SW{50.2}   & \SW{32.2}   &  \SW{42.1}  & \SW{86.7} & 50.7& 41.2\\%  & \SW{21.2} \\
     \hline
  \end{tabular}
  \caption{Translation performance with automatic domains, computed with the original test sets.}
  \label{tab:subdomains}
  \fyDone{Fill the table with correct results,}
\end{table*}

Table~\ref{tab:subdomains} reports the effect of using automatic domain tags on the 6 domain-specific test sets: each sentence was first assigned to an automatic class, translated with the corresponding multi-domain system; aggregate numbers were then computed, as well as comparisons with the 6-domain scenarios. The results are very clear and confirm previous observations: even though some clusters are very close, the net effect is a decrease in performance for almost all systems and conditions. In this setting, the best MDMT of our pool (MDL-Res) is no longer able to surpass the \system{Mix-Nat} baseline.\fyTodo{Note about scaling?}\fyTodo{More comparison?}

>>>>

\begin{table*}
  \centering
  \fyDone{Fix column size}
  \begin{tabular}{|p{3cm}|*{8}{r|}} \hline
%     &&&&&& \\
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{\domain{avg}} & \multicolumn{1}{c||}{w\domain{avg}} \\ \hline % & \multicolumn{1}{c|}{\domain{news}} 
  %    \system{Mixed-Nat}  & 37.3 & 54.6 & 50.1 & 33.5 & 43.2 & 77.5  & 41.1  & 49.4 \\% & 23.5\\
  %     \system{FT-Full}       & 37.7 & \SB{59.2} & \SB{54.5} & 34.0 & \SB{46.8} & \SB{90.8}   & 42.8 & 53.8\\
  %   Full-finetuned on extended in-domain corpora (news) & && 33.96&&& & &\\nn
    \system{DC-Tag}       & 38.5 & \SW{54.0} & 49.0   & 33.6 & \SW{42.2} & \SW{76.7} & 49.0 & 41.6 \\%    & 21.8 \\
    \system{DC-Feat}      & 37.3  & 54.2 & 49.3   & 33.6 & \SW{41.9} & \SW{75.8} & 48.3 & 40.7  \\% & \SW{21.7} \\
    \system{LDC-Tag}     & 37.4   & 54.1 & \SW{48.7} & \SW{32.5} & \SW{41.4} & \SW{75.9} & 48.3 & 39.1         \\% & 22.1 \\ 
    \system{TTM}            & 37.4 & \SW{53.7} & 48.9 & 32.8 & 41.3 & \SW{75.8} & 48.3 & 40.7   \\% &  23.4 \\
    \system{DM}             & 35.4 & 49.3  & 45.2 & 29.7 & 37.1 & \SW{60.0} & 42.8 & 37.8 \\ % & 22.6\\
    \system{ADM}           & 36.1 & 53.5  & 48.0 & 32.0 & 41.1 & 72.1 & 47.1 & 39.5\\% & 23.3 \\
    \system{WDCMT}       & 36.0 & 53.8 & 48.5 & 31.0 & 39.0 & 63.5 & 45.3 & 39.1\\ % & 20.4 \\
    \system{MDL Res}     & 37.3 & 55.5  & \SW{50.2}   & \SW{32.2}   &  \SW{42.1}  & \SW{86.7} & 50.7& 41.2\\%  & \SW{21.2} \\
     \hline
  \end{tabular}
  \caption{Translation performance with automatic domains, computed with the original test sets.}
  \label{tab:subdomains}
  \fyDone{Fill the table with correct results,}
\end{table*}

Table~\ref{tab:subdomains} reports the effect of using automatic domain tags on the 6 domain-specific test sets: each sentence was first assigned to an automatic class, translated with the corresponding multi-domain system; aggregate numbers were then computed, as well as comparisons with the 6-domain scenarios. The results are very clear and confirm previous observations: even though some clusters are very close, the net effect is a decrease in performance for almost all systems and conditions. In this setting, the best MDMT in our pool (MDL-Res) is no longer able to surpass the \system{Mix-Nat} baseline.\fyTodo{Note about scaling?}\fyTodo{More comparison?}
